% Slide 5: Related Works & Contributions
\begin{frame}{\ModuleFrameTitle{2}{Related Works \& Contributions}}
\begin{columns}[T,totalwidth=\textwidth]

% ---- Left column: related works --------------------------------------
\column{0.50\textwidth}

{\small\textbf{Related Works}}

\vspace{0.10cm}
{\small\begin{itemize}
  \item \textbf{1. The Problem: Grid Exploration}
        \newline {\footnotesize\textcolor{softgray}{[Bramas et al., Sardar et al.]}}
        \newline $\rightarrow$ Luminous robot models explore empty grids; obstacle models use completely different assumptions.
  
  \item \textbf{2. Generation: Hand vs. Synthesis}
        \newline {\footnotesize\textcolor{softgray}{[Bonnet et al., Millet et al.]}}
        \newline $\rightarrow$ Manual design is error-prone. Automated synthesis suffers from combinatorial explosion (limited to rings).

  \item \textbf{3. Validation: Formal Verification}
        \newline {\footnotesize\textcolor{softgray}{[Bérard et al., Courtieu et al.]}}
        \newline $\rightarrow$ Proof Assistants require manual human effort. Model Checking is strictly restricted to small graphs.
\end{itemize}

}

% ---- Right column: contributions -------------------------------------
\column{0.46\textwidth}

{\small\textbf{Our Contributions}}

\vspace{0.10cm}
{\small\begin{itemize}
  \item \textcolor{accent}{\textbf{The Problem:}} First generic methodology for synthesizing perpetual exploration algorithms in grids containing an obstacle.
  \item \textcolor{accent}{\textbf{The Generation:}} Scenario-guided synthesis to overcome the state-space explosion of standard controller synthesis.
  \item \textcolor{accent}{\textbf{The Validation:}} Partly automated pipeline using small-grid simulations generalized by a mathematical induction proof.
\end{itemize}
}

\end{columns}
\end{frame}